---
title: "HW 1"
output: github_document
name: Wenyan Ma
uni: wm2460
---

```{r setup, include=FALSE}
data("penguins", package = "palmerpenguins")
library(tidyverse)
library(tibble)
```


## Problem 1

#### Description of "penguins" dataset

The name of the penguins dataset is `r names(penguins)`.
This data set contains physical traits information about the different species of penguins in some islands. 

There are `r nrow(penguins)` observations and `r ncol(penguins)` variables in this dataset. 

The means flipper length is `r mean(pull(penguins,flipper_length_mm), na.rm = TRUE)`


#### Scatterplot

```{r scatterplot_penguins}

penguins_plot_df = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  Species = penguins$species
)

ggplot(penguins_plot_df, aes(x = x, y = y, color = Species)) + geom_point()

ggsave("penguins_plot.pdf", height = 4, width = 6)
```



## Problem 2

#### Data frame & mean calculation

```{r problem_2}
problem2_df = tibble(
  norm_samp = rnorm(10, mean = 0, sd = 1),
  vec_logical = norm_samp > 0,
  vec_char = c("One", "Two", "Three", "Four", "Five", "Six", "Seven", "Eight", "Nine", "Ten"),
  vec_factor = factor(c("High", "Low", "Low", "Medium", "High", "High", "Medium", "Medium", "Low", "Medium"))
)

problem2_df

mean(problem2_df$norm_samp)
mean(problem2_df$vec_logical)
mean(problem2_df$vec_char)
mean(problem2_df$vec_factor)

```

In this dataframe, we can calculate the mean if the vector is numeric or logical, and we cannot calculate the mean when the vector is character or factor. 

#### Convert variable & discussion
```{r convert_variables}

#Convert logical to numeric
convert_logical = as.numeric(problem2_df$vec_logical)

#Convert character to numeric
convert_char = as.numeric(problem2_df$vec_char)

#Convert factor to numeric
convert_factor = as.numeric(problem2_df$vec_factor)

```

Using thr `as.numeric` function, I was able to convert logical and factor vectors into numeric vector. However, when I tried to convert the character vector, I received the warning message saying `"NAs introduced by coercion"`. 

For logical vector, the option is either `TRUE` or `FALSE`. So R assigns numeric value to these two options and we are able to find the means of the logical vector. 

For character vector, it is impossible to calculate the mean or convert it to numeric and calculate the mean. 

For factor vector, since there are 3 "levels" in the dataframe, it is possible to convert it into a numeric vector and calculate mean that way. 
