---
title: "HW 1"
output: github_document
---

```{r setup, include=FALSE}
data("penguins", package = "palmerpenguins")
library(tidyverse)
library(tibble)
```


## Problem 1

#### Description of "penguins" dataset

The name of the penguins dataset are `r names(penguins)`.
This data set contains physical traits information about the different species of penguins in some islands. 


There are `r nrow(penguins)` observations and `r ncol(penguins)` variables in this dataset. 


```{r}
mean(penguins$flipper_length_mm,na.rm = TRUE)
```


The means flipper length is `mean(pull(.penguins, var = flipper_length_mm))`

The means flipper length is `r mean(pull(penguins,flipper_length_mm), na.rm = TRUE)`


#### Scatterplot

```{r scatterplot_penguins}

penguins_plot_df = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  Species = penguins$species
)

ggplot(penguins_plot_df, aes(x = x, y = y, color = Species)) + geom_point()
```

ggsave("penguins_plot.pdf", height = 4, width = 6)



## Problem 2

```{r problem_2}
p2_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  
)
```


