---
title: "HW 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data("penguins", package = "palmerpenguins")
library(tidyverse)
library(tibble)

```


## Question 1

#### Description of "penguins" dataset

The name of the penguins dataset are `r names(penguins)`.
This data set contains physical traits information about the different species of penguins in some islands. 


There are `r nrow(penguins)` observations and `r ncol(penguins)` variables in this dataset. 


```{r}
mean(penguins$flipper_length_mm,na.rm = TRUE)
```


The means flipper length is 200.9152.

#### Scatterplot


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
