---
title: "P8105_hw1_wm2460"
output: github_document
name: Wenyan Ma
uni: wm2460
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
data("penguins", package = "palmerpenguins")
library(tidyverse)
```



## Problem 1

#### Description of the "penguins" dataset


The "penguins" dataset is shown here:

```{r penguins_description}
head(penguins)
```

The variable names of the penguins dataset are `r names(penguins)`.

This data set contains physical traits measurement information about the different species of penguins on some islands. Some important variables that measure the physical characteristics of penguins include `flipper_length_mm`, `bill_length_mm`, `bill_depth_mm`, and `body_mass_g`. 

There are `r nrow(penguins)` observations and `r ncol(penguins)` variables in this dataset. 

The means flipper length is `r mean(pull(penguins,flipper_length_mm), na.rm = TRUE)`


#### Scatterplot

```{r scatterplot_penguins}

penguins_plot_df = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  Species = penguins$species
)

ggplot(penguins_plot_df, aes(x = x, y = y, color = Species)) + geom_point()

ggsave("penguins_plot.pdf", height = 4, width = 6)
```


## Problem 2

#### Data frame & mean calculations

```{r problem_2}
problem2_df = tibble(
  norm_samp = rnorm(10, mean = 0, sd = 1),
  vec_logical = norm_samp > 0,
  vec_char = c("One", "Two", "Three", "Four", "Five", "Six", "Seven", "Eight", "Nine", "Ten"),
  vec_factor = factor(c("High", "Low", "Low", "Medium", "High", "High", "Medium", "Medium", "Low", "Medium"))
)

problem2_df

mean(problem2_df$norm_samp)
mean(problem2_df$vec_logical)
mean(problem2_df$vec_char)
mean(problem2_df$vec_factor)

```

In this data frame, we can calculate the mean if the vector is numeric or logical, and we cannot calculate the mean when the vector is a character or factor. 

#### Convert variables & discussions

```{r convert_variables}

#Convert logical to numeric
convert_logical = as.numeric(problem2_df$vec_logical)

#Convert character to numeric
convert_char = as.numeric(problem2_df$vec_char)

#Convert factor to numeric
convert_factor = as.numeric(problem2_df$vec_factor)

```

Using the `as.numeric` function, I was able to convert logical and factor vectors into numeric vectors. However, when I tried to convert the character vector, I received the warning message saying `"NAs introduced by coercion"`. 

For the logical vector, the option is either `TRUE` or `FALSE`. So, R can assign numeric values to these two options, and we are able to find the means of the logical vector. 

For the character vector, it is impossible to calculate the mean or convert it to a numeric vector and calculate the mean that way. 

For the factor vector, since there are 3 "levels" (i.e., "Low", "Medium", "High") in the data frame, it is possible to convert the factor vector into a numeric vector by assigning numbers to each level and calculate the mean that way. 

Therefore, the properties of different variable types and the process of converting variables helped explain what happens when I try to take the mean.


#### End of HW 1


